---
title: "ESM 206 Assignment 5"
author: "Ruoyu Wang & Haley Grant"
date: "11/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(janitor)
library(ggbeeswarm)
library(car)
library(kableExtra)
library(janitor)
```

#### Introduction

#### Data and Methods

#### Results

##### Results A: Visually compare annual salamander counts in old growth (OG) and clear cut (CC) sections of Mack Creek. 

DITE = pacific giant salamander

1993 = beginning of pacific giant salamander

```{r}

# Read in data

mack_creek_df <- read_csv("mack_creek_vertebrates.csv") %>% 
  clean_names()

```

```{r} 

# Data wrangling

mack_creek_a <- mack_creek_df %>% 
  filter(year > 1992) %>%
  filter(species == "DITE") %>% 
  group_by(year, section) %>% 
  summarize(total_count <- sum(!is.na(species))) %>% 
  rename(total_count = "total_count <- sum(!is.na(species))")

```

```{r}

# Create a finalized graph

ggplot(mack_creek_a, aes(x = year, y = total_count)) +
  geom_point(aes(color = section))

```

```{r}



```


##### Results B
##### Results C
##### Results D
##### Results E

- 
- 
- 

#### Summary

#### References 

Gregory S. V. 2016. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present. Environmental Data Initiative. https://doi.org/10.6073/pasta/5de64af9c11579266ef20da2ff32f702.







